%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.90]{geometry} % Control document margins
\setlength{\hintscolumnwidth}{3cm} % Change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%\usepackage[english]{babel}
%\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[english]{babel}
\usepackage{etaremune}  % for reverse enumeration
\usepackage{enumitem} % for different style in itemize

% footer page count
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}

\cfoot{\thepage\ of \pageref{LastPage}}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{André} % Your first name
\familyname{F. Rendeiro} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Computational biologist}
%\address{}
%\mobile{}
%\phone{}
%\fax{}
\email{andre.rendeiro@pm.me}
\homepage{andre-rendeiro.com} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example

\social[orcid][orcid.org/0000-0001-9362-5373]{ORCID: 0000-0001-9362-5373}
\social[github]{afrendeiro}
\social[twitter]{afrendeiro}


%\extrainfo{additional information}
%\photo[70pt][0.4pt]{/home/afr/Pictures/me.png} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   CURRENT POSITION
%----------------------------------------------------------------------------------------

\section{Current position}
    \cventry{03/2020 - present}
    {Postdoctoral Associate in Computational Biomedicine}{Institute of Computational Biomedicine, Englander Institute for Precision Medicine, Weill Cornell Medicine}{USA}
    {}{Supervisor: Olivier Elemento}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
    \cventry{09/2014 - 01/2020}
        {PhD}{Medical University of Vienna}{Austria}{}{Supervisor: Christoph Bock, CeMM Research Centre for Molecular Medicine}
    \cventry{09/2012 - 06/2014}
        {'Mestrado' (MSc) in Molecular and Cell Biology}{University of Aveiro}{Portugal}{}{}
    \cventry{09/2008 - 07/2012}
        {'Licenciatura' (BSc) in Biology}{University of Aveiro}{Portugal}{}{}


%----------------------------------------------------------------------------------------
%   KEY PUBLICATIONS
%----------------------------------------------------------------------------------------


\section{Key publications}
    \cvitem{}
        {\underline{Rendeiro}*, Ravichandran* \textit{et al.}, \textbf{The spatial landscape of lung pathology during COVID-19 progression}. Nature (2021) \href{https://dx.doi.org/10.1038/s41586-021-03475-6}{doi:10.1038/s41586-021-03475-6}}
    \cvitem{}
        {\underline{Rendeiro}*, Krausgruber* \textit{et al.}, \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of ibrutinib drug response in CLL}. Nature Communications (2020). \href{https://dx.doi.org/10.1038/s41467-019-14081-6}{doi:10.1038/s41467-019-14081-6}}
    \cvitem{}{
        Datlinger*, \underline{Rendeiro}*, \textit{et al}. \textbf{Ultra-high throughput single-cell RNA sequencing by combinatorial fluidic indexing}. bioRxiv (2019). \href{https://dx.doi.org/10.1101/2019.12.17.879304}{doi:10.1101/2019.12.17.879304}
    }
    \cvitem{}{
        Datlinger, \underline{Rendeiro}*, Schmidl* \textit{et al.}, \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. Nature Methods (2017) \href{https://dx.doi.org/10.1038/nmeth.4177}{doi:10.1038/nmeth.4177}
    }
    \cvitem{}{
        \underline{Rendeiro}*, Schmidl*, Strefford* \textit{et al.}, \textbf{Chromatin accessibility maps of chronic lymphocytic leukaemia identify subtype-specific epigenome signatures and transcription regulatory networks}. Nature Communications (2016). \href{https://dx.doi.org/10.1038/ncomms11938}{doi:10.1038/ncomms11938}
    }
    \cvitem{}{
        * \textit{equal contributions}
    }

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Scholarships/Grants}
    \cventry{10/2020 - present}
        {Molecular and Translational Oncology Research}{Training Grant}{T32CA203702}{}{National Cancer Institute, USA}
    \cventry{08/2013 - 06/2014}
        {Erasmus studies mobility program scholarship}{}{}{}{European Commission}
    \cventry{09/2011 - 06/2012}
        {Erasmus intership mobility program scholarship}{}{}{}{European Commission}
    \cventry{10/2009 - 06/2010}
        {"Integration into Research" Grant}{}{}{}{Science and Technology Foundation, Portugal}

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------
\newpage

\section{All publications}
    \cvitem{\underline{Peer reviewed publications}}{}
        \begin{etaremune}[leftmargin=1.0cm, itemindent=0pt, topsep=10pt, itemsep=2pt, partopsep=0pt, parsep=0pt]

        \item Paul Datlinger*, \underline{André F. Rendeiro}*, Thorina Boenke, Thomas Krausgruber, Daniele Barreca, Christoph Bock. \textbf{Ultra-high throughput single-cell RNA sequencing by combinatorial fluidic indexing}. Nature Methods (2021). \href{https://dx.doi.org/10.1038/s41592-021-01153-z}{doi:10.1038/s41592-021-01153-z}

        \item Peter Peneder, Adrian Stütz, Didier Surdez, Manuela Krumbholz, Sabine Semper, Mathieu Chicard, Nathan Sheffield, Gaelle Pierron, Eve Lapouble, Marcus Tötzl, Bekir Ergüner, Daniele Barreca, \underline{André F. Rendeiro}, Abbas Agaimy, Heidrun Boztug, Gernot Engstler, Michael Dworzak, Marie Bernkopf, Sabine Taschner-Mandl, Inge Ambros, Ola Myklebost, Perrine Marec-Berard, Susan Burchill, Bernadette Brennan, Sandra Strauss, Jeremy Whelan, Gudrun Schleiermacher, Christiane Schaefer, Uta Dirksen, Caroline Hutter, Kjetil Boye, Peter Ambros, Olivier Delattre, Markus Metzler, Christoph Bock, Eleni Tomazou. \textbf{Multimodal analysis of cell-free DNA whole genome sequencing for pediatric cancers with low mutational burden}. Nature Communications (2021). \href{https://dx.doi.org/10.1038/s41467-021-23445-w}{doi:10.1038/s41467-021-23445-w}

        \item Johannes C. Melms*, Jana Biermann*, Huachao Huang*, Yiping Wang*, Ajay Nair*, Somnath Tagore*, Igor Katsyv*, \underline{André F. Rendeiro}*, Amit Dipak Amin*, Denis Schapiro, Chris J. Frangieh, Adrienne M. Luoma, Aveline Filliol, Yinshan Fang, Hiranmayi Ravichandran, Mariano G. Clausi, George A. Alba, Meri Rogava, Sean W. Chen, Patricia Ho, Daniel T. Montoro, Adam E. Kornberg, Arnold S. Han, Mathieu F. Bakhoum, Niroshana Anandasabapathy, Mayte Suárez-Fariñas, Samuel F. Bakhoum, Yaron Bram, Alain Borczuk, Xinzheng V.Guo, Jay H. Lefkowitch, Charles Marboe, Stephen. M. Lagana, Armando Del Portillo, Emmanuel Zorn, Glen S. Markowitz, Robert F. Schwabe, Robert E. Schwartz, Olivier Elemento, Anjali Saqi, Hanina Hibshoosh, Jianwen Que, Benjamin Izar. \textbf{A molecular single-cell lung atlas of lethal COVID-19}. Nature (2021). \href{https://dx.doi.org/10.1038/s41586-021-03569-1}{doi:10.1038/s41586-021-03569-1}

        \item \underline{André F. Rendeiro}*, Hiranmayi Ravichandran*, Yaron Bram, Vasuretha Chandar, Junbum Kim, Cem Meydan, Jiwoon Park, Jonathan Foox, Tyler Hether, Sarah Warren, Youngmi Kim, Jason Reeves, Steven Salvatore, Christopher E. Mason, Eric C. Swanson, Alain C. Borczuk, Olivier Elemento, Robert E. Schwartz. \textbf{The spatial landscape of lung pathology during COVID-19 progression}. Nature (2021). \href{https://dx.doi.org/10.1038/s41586-021-03475-6}{doi:10.1038/s41586-021-03475-6}

        \item Sandra Schick, Sarah Grosche, Katharina Eva Kohl, Danica Drpic, Martin G. Jaeger, Nara C. Marella, Hana Imrichova, Jung-Ming G. Lin, Gerald Hofstätter, Michael Schuster, \underline{André F. Rendeiro}, Anna Koren, Mark Petronczki, Christoph Bock, André C. Müller, Georg E. Winter, Stefan Kubicek. \textbf{Acute BAF perturbation causes immediate changes in chromatin accessibility}. Nature Genetics (2021). \href{https://dx.doi.org/10.1038/s41588-021-00777-3}{doi:10.1038/s41588-021-00777-3}
    
        \item \underline{André F. Rendeiro}, Joseph Casano, Charles Kyriakos Vorkas, Harjot Singh, Ayana Morales, Robert A DeSimone, Grant B Ellsworth, Rosemary Soave, Shashi N Kapadia, Kohta Saito, Christopher D Brown, JingMei Hsu, Christopher Kyriakides, Steven Chui, Luca Cappelli, Maria Teresa Cacciapuoti, Wayne Tam, Lorenzo Galluzzi, Paul D Simonson, Olivier Elemento, Mirella Salvatore, Giorgio Inghirami. \textbf{Profiling of immune dysfunction in COVID-19 patients allows early prediction of disease progression}. Life Science Alliance (2020). \href{https://dx.doi.org/10.26508/lsa.202000955}{doi:10.26508/lsa.202000955}

        \item Alexander Swoboda, Robert Soukup, Oliver Eckel, Katharina Kinslechner, Bettina Wingelhofer, David Schörghofer, Christina Sternberg, Ha T T Pham, Maria Vallianou, Jaqueline Horvath, Dagmar Stoiber, Lukas Kenner, Lionel Larue, Valeria Poli, Friedrich Beermann, Takashi Yokota, Stefan Kubicek, Thomas Krausgruber, \underline{André F. Rendeiro}, Christoph Bock, Rainer Zenz, Boris Kovacic, Fritz Aberger, Markus Hengstschläger, Peter Petzelbauer, Mario Mikula, Richard Moriggl. \textbf{STAT3 promotes melanoma metastasis by CEBP-induced repression of the MITF pathway}. Nature (2020).
        \href{https://dx.doi.org/10.1038/s41388-020-01584-6}{doi:10.1038/s41388-020-01584-6}

        \item Thomas Krausgruber, Nikolaus Fortelny, Victoria Fife-Gernedl, Martin Senekowitsch, Linda C. Schuster, Alexander Lercher, Amelie Nemc, Christian Schmidl, \underline{André F. Rendeiro}, Andreas Bergthaler, Christoph Bock. \textbf{Structural cells are key regulators of organ-specific immune responses}. Nature (2020).
        \href{https://dx.doi.org/10.1038/s41586-020-2424-4}{doi:10.1038/s41586-020-2424-4}

        \item Rainer Hubmann, Susanne Schnabl, Mohammad Araghi, Christian Schmidl, \underline{André F. Rendeiro}, Martin Hilgarth, Dita Demirtas, Farghaly Ali,Philipp B. Staber, Peter Valent, Christoph Zielinski, Ulrich Jäger, Medhat Shehata. \textbf{Targeting Nuclear NOTCH2 by Gliotoxin Recovers a Tumor-Suppressor NOTCH3 Activity in CLL}. Cells (2020).
        \href{http://dx.doi.org/10.3390/cells9061484}{doi:10.3390/cells9061484}

        \item Elizabeth C Rosser, Christopher J.M. Piper, Diana E Matei ,Paul A. Blair, \underline{André F. Rendeiro}, Michael Orford, Dagmar G. Alber, Thomas Krausgruber, Diego Catalan, Nigel Klein, Jessica J. Manson, Ignat Drozdov, Christoph Bock, Lucy R Wedderburn, Simon Eaton, Claudia Mauri. \textbf{Microbiota-Derived Metabolites Suppress Arthritis by Amplifying Aryl-Hydrocarbon Receptor Activation in Regulatory B Cells}. Cell Metabolism (2020).
        \href{https://dx.doi.org/10.1016/j.cmet.2020.03.003}{doi:10.1016/j.cmet.2020.03.003}

        \item \underline{André F. Rendeiro}*, Thomas Krausgruber*, Nikolaus Fortelny, Fangwen Zhao, Thomas Penz, Matthias Farlik, Linda C. Schuster, Amelie Nemc, Szabolcs Tasnády, Marienn Réti, Zoltán Mátrai, Donat Alpar, Csaba Bödör, Christian Schmidl, Christoph Bock, \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of ibrutinib drug response in CLL}. Nature Communications (2020).
        \href{https://dx.doi.org/10.1038/s41467-019-14081-6}{doi:10.1038/s41467-019-14081-6}

        \item Michael Delacher, Charles D Imbusch, Agnes Hotz-Wagenblatt, Jan-Philipp Mallm, Katharina Bauer, Malte Simon, Dania Riegel, \underline{André F. Rendeiro}, Sebastian Bittner, Lieke Sanderink, Asmita Pant, Lisa Schmidleithner, Kathrin L Braband, Bernd Echtenachter, Alexander Fischer, Valentina Giunchiglia, Petra Hoffmann, Matthias Edinger, Christoph Bock, Michael Rehli, Benedikt Brors, Christian Schmidl, Markus Feuerer. \textbf{Precursors for Nonlymphoid-Tissue Treg Cells Reside in Secondary Lymphoid Organs and Are Programmed by the Transcription Factor BATF}. Immunity (2020).
        \href{https://dx.doi.org/doi:10.1016/j.immuni.2019.12.002}{doi:10.1016/j.immuni.2019.12.002}

        \item Christopher JM Piper, Elizabeth C Rosser, Kristine Oleinika, Kiran Nistala, Thomas Krausgruber, \underline{André F. Rendeiro}, Aggelos Banos, Ignat Drozdov, Matteo Villa, Scott Thomson, Georgina Xanthou, Christoph Bock, Brigitta Stockinger, Claudia Mauri. \textbf{Aryl Hydrocarbon Receptor Contributes to the Transcriptional Program of IL-10-Producing Regulatory B Cells}. Cell Reports (2019).
        \href{https://dx.doi.org/10.1016/j.celrep.2019.10.018}{doi:10.1016/j.celrep.2019.10.018}

        \item Florian Puhm, Taras Afonyushkin, Ulrike Resch, Georg Obermayer, Manfred Rohde, Thomas Penz, Michael Schuster, Gabriel Wagner, \underline{André F. Rendeiro}, Imene Melki, Christoph Kaun, Johann Wojta, Christoph Bock, Bernd Jilma, Nigel Mackman, Eric Boilard, Christoph J Binder. \textbf{Mitochondria are a subset of extracellular vesicles released by activated monocytes and induce type I IFN and TNF responses in endothelial cells}. Circulation Research (2019).
        \href{https://dx.doi.org/10.1161/CIRCRESAHA.118.314601}{doi:10.1161/CIRCRESAHA.118.314601}

        \item Sandra Schick, \underline{André F. Rendeiro}, Kathrin Runggatscher, Anna Ringler, Bernd Boidol, Melanie Hinkel, Peter Májek, Loan Vulliard, Thomas Penz, Katja Parapatics, Christian Schmidl, Jörg Menche, Guido Boehmelt, Mark Petronczki, André C. Müller, Christoph Bock, Stefan Kubicek. \textbf{Systematic characterization of BAF mutations provides insights into intracomplex synthetic lethalities in human cancers}. Nature Genetics (2019).
        \href{https://dx.doi.org/10.1038/s41588-019-0477-9}{doi:10.1038/s41588-019-0477-9}

        \item Sara Sdelci, \underline{André F. Rendeiro}, Philipp Rathert, Wanhui You, Jung-Ming G. Lin, Anna Ringler, Gerald Hofstätter, Herwig P. Moll, Bettina Gürtl, Matthias Farlik, Sandra Schick, Freya Klepsch, Matthew Oldach, Pisanu Buphamalai, Fiorella Schischlik, Peter Májek, Katja Parapatics, Christian Schmidl, Michael Schuster, Thomas Penz, Dennis L. Buckley, Otto Hudecz, Richard Imre, Shuang-Yan Wang, Hans Michael Maric, Robert Kralovics, Keiryn L. Bennett, Andre C. Müller, Karl Mechtler, Jörg Menche, James E. Bradner, Georg E. Winter, Kristaps Klavins, Emilio Casanova, Christoph Bock, Johannes Zuber, Stefan Kubicek. \textbf{MTHFD1 interaction with BRD4 links folate metabolism to transcriptional regulation}. Nature Genetics (2019).
        \href{https://dx.doi.org/10.1038/s41588-019-0413-z}{doi:10.1038/s41588-019-0413-z}

        \item Christian Schmidl*, Gregory I Vladimer*, \underline{André F. Rendeiro}*, Susanne Schnabl*, Thomas Krausgruber, Christina Taubert, Nikolaus Krall, Tea Pemovska, Mohammad Araghi, Berend Snijder, Rainer Hubmann, Anna Ringler, Kathrin Runggatscher, Dita Demirtas, Oscar Lopez de la Fuente, Martin Hilgarth, Cathrin Skrabs, Edit Porpaczy, Michaela Gruber, Gregor Hoermann, Stefan Kubicek, Philipp B Staber, Medhat Shehata, Giulio Superti-Furga, Ulrich Jäger, Christoph Bock. \textbf{Combined chemosensitivity and chromatin profiling prioritizes drug combinations in CLL}. Nature Chemical Biology (2019).
        \href{https://dx.doi.org/10.1038/s41589-018-0205-2}{doi:10.1038/s41589-018-0205-2}

        \item Tahsin Stefan Barakat, Florian Halbritter, Man Zhang, \underline{André F. Rendeiro}, Christoph Bock, Ian Chambers. (2017). \textbf{Functional dissection of the enhancer repertoire in human embryonic stem cells}. Cell Stem Cell (2018). 10.1016/j.stem.2018.06.014
        \item Paul Datlinger, \underline{André F. Rendeiro}*, Christian Schmidl*, Thomas Krausgruber, Peter Traxler, Johanna Klughammer, Linda C Schuster, Amelie Kuchler, Donat Alpar, Christoph Bock. \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. Nature Methods (2017).
        \href{https://dx.doi.org/10.1038/nmeth.4177}{doi:10.1038/nmeth.4177}

        \item Roman A Romanov, Amit Zeisel, Joanne Bakker, Fatima Girach, Arash Hellysaz, Raju Tomer, Alán Alpár, Jan Mulder, Frédéric Clotman, Erik Keimpema, Brian Hsueh, Ailey K Crow, Henrik Martens, Christian Schwindling, Daniela Calvigioni, Jaideep S Bains, Zoltán Máté, Gábor Szabó, Yuchio Yanagawa, Ming-Dong Zhang, \underline{André F. Rendeiro}, Matthias Farlik, Mathias Uhlén, Peer Wulff, Christoph Bock, Christian Broberger, Karl Deisseroth, Tomas Hökfelt, Sten Linnarsson, Tamas L Horvath, Tibor Harkany. \textbf{Molecular interrogation of hypothalamic organization reveals distinct dopamine neuronal subtypes}. Nature Neuroscience (2016).
        \href{https://dx.doi.org/10.1038/nn.4462}{doi:10.1038/nn.4462}

        \item Clara Jana-Lui Busch, Tim Hendrikx, David Weismann, Sven Jäckel, Sofie M. A. Walenbergh, \underline{André F. Rendeiro}, Juliane Weißer, Florian Puhm, Anastasiya Hladik, Laura Göderle, Nikolina Papac-Milicevic, Gerald Haas, Vincent Millischer, Saravanan Subramaniam, Sylvia Knapp, Keiryn L. Bennett, Christoph Bock, Christoph Reinhardt, Ronit Shiri-Sverdlov, Christoph J. Binder. \textbf{Malondialdehyde epitopes are sterile mediators of hepatic inflammation in hypercholesterolemic mice}. Hepatology (2017).
        \href{https://dx.doi.org/10.1002/hep.28970}{doi:10.1002/hep.28970}

        \item \underline{André F. Rendeiro}*, Christian Schmidl*, Jonathan C. Strefford*, Renata Walewska, Zadie Davis, Matthias Farlik, David Oscier, Christoph Bock. \textbf{Chromatin accessibility maps of chronic lymphocytic leukaemia identify subtype-specific epigenome signatures and transcription regulatory networks}. Nature Communications. 7:11938 (2016).
        \href{https://dx.doi.org/10.1038/ncomms11938}{doi:10.1038/ncomms11938}

        \item Christian Schmidl*, \underline{André F. Rendeiro}*,  Nathan C Sheffield, Christoph Bock. 2015. \textbf{ChIPmentation: fast, robust, low-input ChIP-seq for histones and transcription factors}. Nature Methods (2015).
        \href{https://dx.doi.org/10.1038/nmeth.3542}{doi:10.1038/nmeth.3542}

        \item Michaela Schwaiger, Anna Schönauer, \underline{André F. Rendeiro}, Carina Pribitzer, Alexandra Schauer, Anna Gilles, Johannes Schinko, David Fredman, and Ulrich Technau. \textbf{Evolutionary conservation of the eumetazoan gene regulatory landscape}. Genome Research (2014).
        \href{https://dx.doi.org/10.1101/gr.162529.113}{doi:10.1101/gr.162529.113}

        \end{etaremune}

    \cvitem{\underline{Preprints}}{(does not include preprints later published in peer-reviewed journals)}
        \begin{etaremune}[leftmargin=1.0cm, itemindent=0pt, topsep=10pt, itemsep=2pt, partopsep=0pt, parsep=0pt]

        \item Nathan C. Sheffield, Michał Stolarczyk, Vincent P. Reuter, \underline{André F. Rendeiro}. \textbf{Linking big biomedical datasets to modular analysis with Portable Encapsulated Projects}. bioRxiv (2020). \href{https://dx.doi.org/10.1101/2020.10.08.331322}{doi:10.1101/2020.10.08.331322}

        \item \underline{André F. Rendeiro}, Pavla  Navratilova, Eric Thompson (2014). \textbf{Chromatin preparation for ChIP-seq in \textit{Oikopleura dioica}}. figshare. \href{https://doi.org/10.6084/m9.figshare.884562}{doi:10.6084/m9.figshare.884562}
        \end{etaremune}

\section{Communications}
    \cvitem{\underline{Conference talks}}{}
        \begin{etaremune}[leftmargin=1.0cm,itemindent=0pt,topsep=10pt,itemsep=2pt,partopsep=0pt,parsep=0pt]
        \item
        %\underline{André F. Rendeiro}.
        \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of Ibrutinib response in CLL}. \textit{Young Scientist Association of the Medical University of Vienna PhD Symposia}, June 2019, Vienna, Austria.
        \item
        %\underline{André F. Rendeiro}.
        \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of Ibrutinib response in CLL}. \textit{Frontiers in Single Cell Genomics Meeting - Cold Spring Harbour Asia}, November 2018, Suzhou, China.
        \item
        %\underline{André F. Rendeiro}.
        \textbf{CROP-seq: updates on the single cell CRISPR screening method}. \textit{10X User Group Meeting 2018}, April 2018, EMBL, Heidelberg, Germany.
        \item
        %\underline{André F. Rendeiro}.
        \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. \textit{SLAS 2018}, February 2018, San Diego, USA.
        %\item
        %\underline{André F. Rendeiro}.
        \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. \textit{Illumina User Group Meeting 2017}, February 2018, Bern, Switzerland.
        \item
        %\underline{André F. Rendeiro}.
        \textbf{Large-scale ATAC-seq profiling to identify disease subtypes, regulatory networks and monitoring treatment in CLL}. \textit{Illumina User Group Meeting 2017}, February 2018, Cologne, Germany.
        \item
        %Paul Datlinger, \underline{André F. Rendeiro}*, Christian Schmidl*, Thomas Krausgruber, Peter Traxler, Johanna Klughammer, Linda C Schuster, Amelie Kuchler, Donat Alpar, Christoph Bock.
        \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. \textit{Ascona Workshop 2017}, May 2017, Ascona, Switzerland.
        \item
        %Michaela Schwaiger, Anna Schönauer, \underline{André F. Rendeiro}, Carina Pribitzer, Alexandra Schauer, Anna Gilles, Johannes Schinko, David Fredman, and Ulrich Technau.
        \textbf{Evolutionary conservation of the eumetazoan gene regulatory landscape}. \textit{XVIII Portuguese Genetics Society Meeting}, June 2013. Porto, Portugal
        \end{etaremune}

    \cvitem{\underline{Conference posters}}{}
        \begin{etaremune}[leftmargin=1.0cm,itemindent=0pt,topsep=10pt,itemsep=2pt,partopsep=0pt,parsep=0pt]

        \item
        %\underline{André F. Rendeiro}*, Thomas Krausgruber*, Nikolaus Fortelny, Fangwen Zhao, Thomas Penz, Matthias Farlik, Linda C. Schuster, Amelie Nemc, Szabolcs Tasnády, Marienn Réti, Zoltán Mátrai, Donat Alpar, Csaba Bödör, Christian Schmidl, Christoph Bock.
        \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of ibrutinib drug response in chronic lymphocytic leukemia}. \textit{SCOG Workshop Computational Single Cell Genomics}, May 2019. Munich, Germany. \href{https://doi.org/10.6084/m9.figshare.7892663.v1}{doi:10.6084/m9.figshare.7892663.v1}
        \item
        %Christian Schmidl*, \underline{André F. Rendeiro}*, Gregory I Vladimer*, Thomas Krausgruber, Tea Pemovska, Nikolaus Krall, Berend Snijder, Oscar Lopez de la Fuente, Anna Ringler, Stefan Kubicek, Philipp B. Staber, Medhat Shehata, Giulio Superti-Furga, Ulrich Jäger, Christoph Bock.
        \textbf{Combined chromatin accessibility and chemosensitivity profiling identifies targetable pathways and rational drug combinations in Ibrutinib-treated chronic lymphocytic leukemia}. \textit{Young Scientist Association of the Medical University of Vienna PhD Symposia}, June 2017. Vienna, Austria.
        \item
        %\underline{André F. Rendeiro}*, Christian Schmidl*, Jonathan C. Strefford*, Renata Walewska, Zadie Davis, Matthias Farlik, David Oscier, Christoph Bock.
        \textbf{Large-scale chromatin profiling uncovers heterogeneity of molecular phenotypes and gene regulatory networks of chronic lymphocytic leukemia}. \textit{Young Scientist Association of the Medical University of Vienna PhD Symposia}, June 2016, Vienna, Austria. \href{https://doi.org/10.6084/m9.figshare.3479528.v1}{10.6084/m9.figshare.3479528.v1} \textbf{Best poster award in "Malignant Diseases" category}.
        \item
        %\underline{André F. Rendeiro}*, Christian Schmidl*, Jonathan C. Strefford*, Renata Walewska, Zadie Davis, Matthias Farlik, David Oscier, Christoph Bock.
        \textbf{Large-scale chromatin profiling uncovers heterogeneity of molecular phenotypes and gene regulatory networks of chronic lymphocytic leukemia}. \textit{Keystone Symposia on Chromatin and Epigenetics}, March 2016, Whistler, Vancouver, Canada. https://doi.org/10.6084/m9.figshare.3479528.v1
        \item
        %Anna Schönauer, \underline{André F. Rendeiro}, Michaela Schwaiger, Ulrich Technau.
        \textbf{Identification of cis-regulatory elements in the sea anemone \textit{Nematostella vectensis}}. \textit{Evonet Symposium}, September 2012, Vienna Austria. \href{https://doi.org/10.6084/m9.figshare.107026}{doi:10.6084/m9.figshare.107026}
        \end{etaremune}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Additional experience}

    \subsection{\underline{Research Activity}}

        \cventry{08/2013 - 06/2014}
            {The role of E2F regulation and H3K79 methylation in \textit{Oikopleura dioica}'s cell cycle modes}
            {Sars International Centre for Marine Molecular Biology, Bergen, Norway}{}
            {}
            {Supervisor: Eric Thompson}
            %\{I investigated the molecular mechanisms of alternative cell cycle modes (particularly endocycles) in the chordate \textit{Oikopleura dioica} by performing ChIP-seq on transcription factors involved in cell cycle regulation (E2F). I also studied the role of H3K79me on cell cycle regulation through functional studies on its methyltransferase, Dot1.}

        \cventry{09/2011 - 07/2012}
            {Identification of cis-regulatory elements in \textit{Nematostella vectensis} using ChIP-seq}
            {Dept. of Molecular Evolution and Development, University of Vienna, Austria}{}
            {}
            {Supervisor: Ulrich Technau}
            %\{I performed ChIP-seq of chromatin modifications and other regulatory proteins over several developmental stages of \textit{Nematostella vectensis}, constructed a map of chromatin states and predicted cis-regulatory elements genome-wide. I also tested the function of some of these regions \textit{in vivo} in a reporter assay.}

        \cventry{09/2010 - 06/2011}
            {Tol2-mediated zebrafish transgenesis for studies in protein mistranslation}
            {RNA Biology Laboratory, Biology Department, University of Aveiro, Portugal}{}
            {}
            {Supervisor: Manuel Santos}
            %\{I created transgenic zebrafish that were used as a model for studies in neurodegeneration through protein aggregation. This was caused by increasing the level of translational error (mistranslation) during endogenous protein synthesis. I learned to build plasmid constructs, microinject them in zebrafish and screen for phenotypes.}

        \cventry{09/2009 - 06/2010}
            {Transciptome studies with microarrays in heat-shocked yeast}
            {RNA Biology Laboratory, Biology Department, University of Aveiro, Portugal}{}
            {}
            {Supervisor: Manuel Santos}
            %\{I was involved in the analysis of microarray expression data from yeast under various treatments. I learned to pre-process, normalise and explore data programmatically to detect significant differential gene expression, clustering genes and exploring their ontology across treatments.}

    %----------------------------------------------------------------------------------------
    %   COURSES
    %----------------------------------------------------------------------------------------
    \subsection{\underline{Courses and other scientific activity}}
        \cvitem{04/2021}{Probabilistic Modeling in Genomics, Virtual meeting - Cold Spring Harbor, NY, USA}
        \cvitem{09/2015}{Summer School on Machine Learning for Personalised Medicine - Marie Curie Initial Training Network, Manchester, UK}
        \cvitem{09/2012}{Scientific writing course - University of Aveiro, Portugal}

    %----------------------------------------------------------------------------------------
    %   ADMIN
    %----------------------------------------------------------------------------------------
    \subsection{\underline{Associative/Administrative}}

        \cvitem{09/2010 - 06/2012}{Member of the Biology department counsel, University of Aveiro, Portugal}
        \cvitem{09/2009 - 06/2011}{Member of the undergraduate Biology committee, University of Aveiro, Portugal}

%----------------------------------------------------------------------------------------
%   AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

    \cventry{06/2016}
        {Best poster award - "Malignant diseases" category}{YSA Symposium}{}{}{Young Scientist Association of the Medical University of Vienna}
    \cventry{06/2016}
        {Best artwork award - "Illustrations and digital simulations" category}{ScienceArt Competition of the YSA Symposium}{}{}{Young Scientist Association of the Medical University of Vienna}

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}

\subsection{\underline{Computational Biology}}
    \cvitem{Programming}{
    Experienced in \textit{Python} and \textit{R} programming; Beginner level \textit{Rust} programming;
    \newline
    Competence in software development: version control, testing, continuous integration.}
    \cvitem{Data science}{
        Development of data processing pipelines; Data-driven unsupervised analysis and visualisation; Statistical analysis; Application of unsupervised and supervised machine learning models; Basic experience with Bayesian methods and probabilistic programming}
    \cvitem{Applications}{Image analysis (IMC, IHC, brightfield microscopy); single cell *-seq; flow cytometry; bulk ATAC-/ChIP-/RNA-seq; CRISPR screens}

\subsection{\underline{Molecular Biology}}
    \cvitem{Techniques}{Chromatin IP, ChIP-seq, NGS libraries, Western blotting, PCR, Cloning
    \newline Additional experience in: Chemical screening, Zebrafish and \textit{Nematostella} handling and microinjection, basic experience in immunohistochemistry, fluorescence and confocal microscopy}


%----------------------------------------------------------------------------------------
%   SOFTWARE
%----------------------------------------------------------------------------------------
\section{Software}
% \subsection{\underline{Data processing pipelines}}
% \subsection{}
    \cvitem{IMC}{
        A package for the analysis of imaging mass cytometry data:
        \newline
        \href{https://github.com/ElementoLab/imc}{https://github.com/ElementoLab/imc}
    }
    \cvitem{imcpipeline}{
        A pipeline for the preprocessing of imaging mass cytometry data:
        \newline
        \href{https://github.com/ElementoLab/imcpipeline}{https://github.com/ElementoLab/imcpipeline}
    }
    \cvitem{imctransfer}{
        Program for the robust, parallel transfer of raw IMC data between machines:
        \newline
        \href{https://github.com/ElementoLab/imctransfer}{https://github.com/ElementoLab/imctransfer}
    }
    \cvitem{page-enrichment}{
        A Python implementation of the Parametric Analysis of Gene Set Enrichment (PAGE):
        \newline
        \href{https://github.com/afrendeiro/page-enrichment}{https://github.com/afrendeiro/page-enrichment}
    }
    \cvitem{ngs-toolkit}{
        A toolkit for the analysis of NGS data:
        \newline
        \href{https://github.com/afrendeiro/toolkit}{https://github.com/afrendeiro/toolkit}
    }
    \cvitem{peppy}{
        A package to work with Portable Encapsulated Projects (PEP) in Python:
        \newline
        \href{https://github.com/pepkit/peppy}{https://github.com/pepkit/peppy}
    }
    \cvitem{looper}{
        A job controller for Portable Encapsulated Projects (PEP):
        \newline
        \href{https://github.com/pepkit/looper}{https://github.com/pepkit/looper}
    }
    \cvitem{open\_pipelines}{
        Pipelines for a variety of NGS data:
        \newline
        \href{https://github.com/epigen/open\_pipelines}{https://github.com/epigen/open\_pipelines}
    }
    
    % \cvitem{ngstk}{
    %     A collection of CLI tools for common bioinformatics work callable from Python:
    %     \newline
    %     \href{https://github.com/pepkit/ngstk}{https://github.com/pepkit/ngstk}
    % }
    
% \subsection{\underline{Publications}}
%     \cvitem{doi:x,y,z}{
%         \href{https://github.com/ElementoLab/covid-imc}{https://github.com/ElementoLab/covid-imc}
%         \href{https://github.com/ElementoLab/covid-imc-viz}{https://github.com/ElementoLab/covid-imc-viz}
%     }
%     \cvitem{doi:x,y,z}{
%         \href{https://github.com/ElementoLab/covid-imc}{https://github.com/ElementoLab/covid-imc}
%         \href{https://github.com/ElementoLab/covid-imc-viz}{https://github.com/ElementoLab/covid-imc-viz}
%     }


%----------------------------------------------------------------------------------------
%   MEMBERSHIPS
%----------------------------------------------------------------------------------------

%\section{Associations}
%\cvitem{2020-}{New York Academy of Sciences}
%\cvitem{2015-2018}{European Hematology Association (EHA)}

%----------------------------------------------------------------------------------------
%   LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Portuguese}{\textnormal{Native speaker}}{}
\cvitemwithcomment{English}{\textnormal{Very good}}{}
\cvitemwithcomment{Spanish}{\textnormal{Conversational}}{}
\cvitemwithcomment{German}{\textnormal{Basic}}{Basic words and phrases only}
\cvitemwithcomment{French}{\textnormal{Basic}}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%   INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Other interests}

%\cvlistdoubleitem{Ballroom dancing}{Cinema}
%\cvlistdoubleitem{Singing}{Opera}
%\cvlistdoubleitem{Choral conducting}{Piano playing}


%----------------------------------------------------------------------------------------
%   TIMESTAMP
%----------------------------------------------------------------------------------------
\bigskip
\textit{Updated on 2021/04/29}



%----------------------------------------------------------------------------------------
%   COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-3] % Dummy text

% \makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
