%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.90]{geometry} % Control document margins
\setlength{\hintscolumnwidth}{3cm} % Change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%\usepackage[english]{babel}
%\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[english]{babel}
\usepackage{etaremune}  % for reverse enumeration
\usepackage{enumitem} % for different style in itemize

% footer page count
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}

\cfoot{\thepage\ of \pageref{LastPage}}

%----------------------------------------------------------------------------------------
%   NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{André} % Your first name
\familyname{F. Rendeiro} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Computational biologist}
%\address{}
%\mobile{}
%\phone{}
%\fax{}
\email{andre.rendeiro@pm.me}
\homepage{andre-rendeiro.com} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example

\social[orcid][orcid.org/0000-0001-9362-5373]{ORCID: 0000-0001-9362-5373}
\social[github]{afrendeiro}
\social[twitter]{afrendeiro}


%\extrainfo{additional information}
%\photo[70pt][0.4pt]{/home/afr/Pictures/me.png} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%   KEY PUBLICATIONS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%   PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{List of publications}
    \cvitem{\underline{Peer reviewed publications}}{}
        \begin{etaremune}[leftmargin=1.0cm, itemindent=0pt, topsep=10pt, itemsep=2pt, partopsep=0pt, parsep=0pt]

        \item Laurienne Edgar, Naveed Akbar, Adam T Braithwaite, Thomas Krausgruber, Héctor Gallart-Ayala, Jade Bailey, Alastair L Corbin, Tariq E Khoyratty, Joshua T Chai, Mohammad Alkhalil, \underline{André F. Rendeiro}, Klemen Ziberna, Ritu Arya, Thomas J Cahill, Christoph Bock, Jurga Laurencikiene, Mark J Crabtree, Madeleine E Lemieux, Niels P Riksen, Mihai G Netea, Craig E Wheelock, Keith M Channon, Mikael Rydén, Irina A Udalova, Ricardo Carnicer, Robin P Choudhury. \textbf{Hyperglycaemia Induces Trained Immunity in Macrophages and Their Precursors and Promotes Atherosclerosis}. Circulation (2021).
        \href{https://dx.doi.org/10.1161/CIRCULATIONAHA.120.046464}{doi:10.1161/CIRCULATIONAHA.120.046464}

        \item Paul Datlinger*, \underline{André F. Rendeiro}*, Thorina Boenke, Thomas Krausgruber, Daniele Barreca, Christoph Bock. \textbf{Ultra-high throughput single-cell RNA sequencing by combinatorial fluidic indexing}. Nature Methods (2021).
        \href{https://dx.doi.org/10.1038/s41592-021-01153-z}{doi:10.1038/s41592-021-01153-z}

        \item Peter Peneder, Adrian Stütz, Didier Surdez, Manuela Krumbholz, Sabine Semper, Mathieu Chicard, Nathan Sheffield, Gaelle Pierron, Eve Lapouble, Marcus Tötzl, Bekir Ergüner, Daniele Barreca, \underline{André F. Rendeiro}, Abbas Agaimy, Heidrun Boztug, Gernot Engstler, Michael Dworzak, Marie Bernkopf, Sabine Taschner-Mandl, Inge Ambros, Ola Myklebost, Perrine Marec-Berard, Susan Burchill, Bernadette Brennan, Sandra Strauss, Jeremy Whelan, Gudrun Schleiermacher, Christiane Schaefer, Uta Dirksen, Caroline Hutter, Kjetil Boye, Peter Ambros, Olivier Delattre, Markus Metzler, Christoph Bock, Eleni Tomazou. \textbf{Multimodal analysis of cell-free DNA whole genome sequencing for pediatric cancers with low mutational burden}. Nature Communications (2021).
        \href{https://dx.doi.org/10.1038/s41467-021-23445-w}{doi:10.1038/s41467-021-23445-w}

        \item Johannes C. Melms*, Jana Biermann*, Huachao Huang*, Yiping Wang*, Ajay Nair*, Somnath Tagore*, Igor Katsyv*, \underline{André F. Rendeiro}*, Amit Dipak Amin*, Denis Schapiro, Chris J. Frangieh, Adrienne M. Luoma, Aveline Filliol, Yinshan Fang, Hiranmayi Ravichandran, Mariano G. Clausi, George A. Alba, Meri Rogava, Sean W. Chen, Patricia Ho, Daniel T. Montoro, Adam E. Kornberg, Arnold S. Han, Mathieu F. Bakhoum, Niroshana Anandasabapathy, Mayte Suárez-Fariñas, Samuel F. Bakhoum, Yaron Bram, Alain Borczuk, Xinzheng V.Guo, Jay H. Lefkowitch, Charles Marboe, Stephen. M. Lagana, Armando Del Portillo, Emmanuel Zorn, Glen S. Markowitz, Robert F. Schwabe, Robert E. Schwartz, Olivier Elemento, Anjali Saqi, Hanina Hibshoosh, Jianwen Que, Benjamin Izar. \textbf{A molecular single-cell lung atlas of lethal COVID-19}. Nature (2021).
        \href{https://dx.doi.org/10.1038/s41586-021-03569-1}{doi:10.1038/s41586-021-03569-1}

        \item \underline{André F. Rendeiro}*, Hiranmayi Ravichandran*, Yaron Bram, Vasuretha Chandar, Junbum Kim, Cem Meydan, Jiwoon Park, Jonathan Foox, Tyler Hether, Sarah Warren, Youngmi Kim, Jason Reeves, Steven Salvatore, Christopher E. Mason, Eric C. Swanson, Alain C. Borczuk, Olivier Elemento, Robert E. Schwartz. \textbf{The spatial landscape of lung pathology during COVID-19 progression}. Nature (2021).
        \href{https://dx.doi.org/10.1038/s41586-021-03475-6}{doi:10.1038/s41586-021-03475-6}

        \item Sandra Schick, Sarah Grosche, Katharina Eva Kohl, Danica Drpic, Martin G. Jaeger, Nara C. Marella, Hana Imrichova, Jung-Ming G. Lin, Gerald Hofstätter, Michael Schuster, \underline{André F. Rendeiro}, Anna Koren, Mark Petronczki, Christoph Bock, André C. Müller, Georg E. Winter, Stefan Kubicek. \textbf{Acute BAF perturbation causes immediate changes in chromatin accessibility}. Nature Genetics (2021).
        \href{https://dx.doi.org/10.1038/s41588-021-00777-3}{doi:10.1038/s41588-021-00777-3}

        \item \underline{André F. Rendeiro}, Joseph Casano, Charles Kyriakos Vorkas, Harjot Singh, Ayana Morales, Robert A DeSimone, Grant B Ellsworth, Rosemary Soave, Shashi N Kapadia, Kohta Saito, Christopher D Brown, JingMei Hsu, Christopher Kyriakides, Steven Chui, Luca Cappelli, Maria Teresa Cacciapuoti, Wayne Tam, Lorenzo Galluzzi, Paul D Simonson, Olivier Elemento, Mirella Salvatore, Giorgio Inghirami. \textbf{Profiling of immune dysfunction in COVID-19 patients allows early prediction of disease progression}. Life Science Alliance (2020).
        \href{https://dx.doi.org/10.26508/lsa.202000955}{doi:10.26508/lsa.202000955}

        \item Alexander Swoboda, Robert Soukup, Oliver Eckel, Katharina Kinslechner, Bettina Wingelhofer, David Schörghofer, Christina Sternberg, Ha T T Pham, Maria Vallianou, Jaqueline Horvath, Dagmar Stoiber, Lukas Kenner, Lionel Larue, Valeria Poli, Friedrich Beermann, Takashi Yokota, Stefan Kubicek, Thomas Krausgruber, \underline{André F. Rendeiro}, Christoph Bock, Rainer Zenz, Boris Kovacic, Fritz Aberger, Markus Hengstschläger, Peter Petzelbauer, Mario Mikula, Richard Moriggl. \textbf{STAT3 promotes melanoma metastasis by CEBP-induced repression of the MITF pathway}. Oncogene (2020).
        \href{https://dx.doi.org/10.1038/s41388-020-01584-6}{doi:10.1038/s41388-020-01584-6}

        \item Thomas Krausgruber, Nikolaus Fortelny, Victoria Fife-Gernedl, Martin Senekowitsch, Linda C. Schuster, Alexander Lercher, Amelie Nemc, Christian Schmidl, \underline{André F. Rendeiro}, Andreas Bergthaler, Christoph Bock. \textbf{Structural cells are key regulators of organ-specific immune responses}. Nature (2020).
        \href{https://dx.doi.org/10.1038/s41586-020-2424-4}{doi:10.1038/s41586-020-2424-4}

        \item Rainer Hubmann, Susanne Schnabl, Mohammad Araghi, Christian Schmidl, \underline{André F. Rendeiro}, Martin Hilgarth, Dita Demirtas, Farghaly Ali,Philipp B. Staber, Peter Valent, Christoph Zielinski, Ulrich Jäger, Medhat Shehata. \textbf{Targeting Nuclear NOTCH2 by Gliotoxin Recovers a Tumor-Suppressor NOTCH3 Activity in CLL}. Cells (2020).
        \href{https://dx.doi.org/10.3390/cells9061484}{doi:10.3390/cells9061484}

        \item Elizabeth C Rosser, Christopher J.M. Piper, Diana E Matei ,Paul A. Blair, \underline{André F. Rendeiro}, Michael Orford, Dagmar G. Alber, Thomas Krausgruber, Diego Catalan, Nigel Klein, Jessica J. Manson, Ignat Drozdov, Christoph Bock, Lucy R Wedderburn, Simon Eaton, Claudia Mauri. \textbf{Microbiota-Derived Metabolites Suppress Arthritis by Amplifying Aryl-Hydrocarbon Receptor Activation in Regulatory B Cells}. Cell Metabolism (2020).
        \href{https://dx.doi.org/10.1016/j.cmet.2020.03.003}{doi:10.1016/j.cmet.2020.03.003}

        \item \underline{André F. Rendeiro}*, Thomas Krausgruber*, Nikolaus Fortelny, Fangwen Zhao, Thomas Penz, Matthias Farlik, Linda C. Schuster, Amelie Nemc, Szabolcs Tasnády, Marienn Réti, Zoltán Mátrai, Donat Alpar, Csaba Bödör, Christian Schmidl, Christoph Bock. \textbf{Chromatin mapping and single-cell immune profiling define the temporal dynamics of ibrutinib drug response in CLL}. Nature Communications (2020).
        \href{https://dx.doi.org/10.1038/s41467-019-14081-6}{doi:10.1038/s41467-019-14081-6}

        \item Michael Delacher, Charles D Imbusch, Agnes Hotz-Wagenblatt, Jan-Philipp Mallm, Katharina Bauer, Malte Simon, Dania Riegel, \underline{André F. Rendeiro}, Sebastian Bittner, Lieke Sanderink, Asmita Pant, Lisa Schmidleithner, Kathrin L Braband, Bernd Echtenachter, Alexander Fischer, Valentina Giunchiglia, Petra Hoffmann, Matthias Edinger, Christoph Bock, Michael Rehli, Benedikt Brors, Christian Schmidl, Markus Feuerer. \textbf{Precursors for Nonlymphoid-Tissue Treg Cells Reside in Secondary Lymphoid Organs and Are Programmed by the Transcription Factor BATF}. Immunity (2020).
        \href{https://dx.doi.org/10.1016/j.immuni.2019.12.002}{doi:10.1016/j.immuni.2019.12.002}

        \item Christopher JM Piper, Elizabeth C Rosser, Kristine Oleinika, Kiran Nistala, Thomas Krausgruber, \underline{André F. Rendeiro}, Aggelos Banos, Ignat Drozdov, Matteo Villa, Scott Thomson, Georgina Xanthou, Christoph Bock, Brigitta Stockinger, Claudia Mauri. \textbf{Aryl Hydrocarbon Receptor Contributes to the Transcriptional Program of IL-10-Producing Regulatory B Cells}. Cell Reports (2019).
        \href{https://dx.doi.org/10.1016/j.celrep.2019.10.018}{doi:10.1016/j.celrep.2019.10.018}

        \item Florian Puhm, Taras Afonyushkin, Ulrike Resch, Georg Obermayer, Manfred Rohde, Thomas Penz, Michael Schuster, Gabriel Wagner, \underline{André F. Rendeiro}, Imene Melki, Christoph Kaun, Johann Wojta, Christoph Bock, Bernd Jilma, Nigel Mackman, Eric Boilard, Christoph J Binder. \textbf{Mitochondria are a subset of extracellular vesicles released by activated monocytes and induce type I IFN and TNF responses in endothelial cells}. Circulation Research (2019).
        \href{https://dx.doi.org/10.1161/CIRCRESAHA.118.314601}{doi:10.1161/CIRCRESAHA.118.314601}

        \item Sandra Schick, \underline{André F. Rendeiro}, Kathrin Runggatscher, Anna Ringler, Bernd Boidol, Melanie Hinkel, Peter Májek, Loan Vulliard, Thomas Penz, Katja Parapatics, Christian Schmidl, Jörg Menche, Guido Boehmelt, Mark Petronczki, André C. Müller, Christoph Bock, Stefan Kubicek. \textbf{Systematic characterization of BAF mutations provides insights into intracomplex synthetic lethalities in human cancers}. Nature Genetics (2019).
        \href{https://dx.doi.org/10.1038/s41588-019-0477-9}{doi:10.1038/s41588-019-0477-9}

        \item Sara Sdelci, \underline{André F. Rendeiro}, Philipp Rathert, Wanhui You, Jung-Ming G. Lin, Anna Ringler, Gerald Hofstätter, Herwig P. Moll, Bettina Gürtl, Matthias Farlik, Sandra Schick, Freya Klepsch, Matthew Oldach, Pisanu Buphamalai, Fiorella Schischlik, Peter Májek, Katja Parapatics, Christian Schmidl, Michael Schuster, Thomas Penz, Dennis L. Buckley, Otto Hudecz, Richard Imre, Shuang-Yan Wang, Hans Michael Maric, Robert Kralovics, Keiryn L. Bennett, Andre C. Müller, Karl Mechtler, Jörg Menche, James E. Bradner, Georg E. Winter, Kristaps Klavins, Emilio Casanova, Christoph Bock, Johannes Zuber, Stefan Kubicek. \textbf{MTHFD1 interaction with BRD4 links folate metabolism to transcriptional regulation}. Nature Genetics (2019).
        \href{https://dx.doi.org/10.1038/s41588-019-0413-z}{doi:10.1038/s41588-019-0413-z}

        \item Christian Schmidl*, Gregory I Vladimer*, \underline{André F. Rendeiro}*, Susanne Schnabl*, Thomas Krausgruber, Christina Taubert, Nikolaus Krall, Tea Pemovska, Mohammad Araghi, Berend Snijder, Rainer Hubmann, Anna Ringler, Kathrin Runggatscher, Dita Demirtas, Oscar Lopez de la Fuente, Martin Hilgarth, Cathrin Skrabs, Edit Porpaczy, Michaela Gruber, Gregor Hoermann, Stefan Kubicek, Philipp B Staber, Medhat Shehata, Giulio Superti-Furga, Ulrich Jäger, Christoph Bock. \textbf{Combined chemosensitivity and chromatin profiling prioritizes drug combinations in CLL}. Nature Chemical Biology (2019).
        \href{https://dx.doi.org/10.1038/s41589-018-0205-2}{doi:10.1038/s41589-018-0205-2}

        \item Tahsin Stefan Barakat, Florian Halbritter, Man Zhang, \underline{André F. Rendeiro}, Christoph Bock, Ian Chambers. \textbf{Functional dissection of the enhancer repertoire in human embryonic stem cells}. Cell Stem Cell (2017).
        \href{https://dx.doi.org/10.1016/j.stem.2018.06.014}{doi:10.1016/j.stem.2018.06.014}

        \item Paul Datlinger, \underline{André F. Rendeiro}*, Christian Schmidl*, Thomas Krausgruber, Peter Traxler, Johanna Klughammer, Linda C Schuster, Amelie Kuchler, Donat Alpar, Christoph Bock. \textbf{Pooled CRISPR screening with single-cell transcriptome readout}. Nature Methods (2017).
        \href{https://dx.doi.org/10.1038/nmeth.4177}{doi:10.1038/nmeth.4177}

        \item Roman A Romanov, Amit Zeisel, Joanne Bakker, Fatima Girach, Arash Hellysaz, Raju Tomer, Alán Alpár, Jan Mulder, Frédéric Clotman, Erik Keimpema, Brian Hsueh, Ailey K Crow, Henrik Martens, Christian Schwindling, Daniela Calvigioni, Jaideep S Bains, Zoltán Máté, Gábor Szabó, Yuchio Yanagawa, Ming-Dong Zhang, \underline{André F. Rendeiro}, Matthias Farlik, Mathias Uhlén, Peer Wulff, Christoph Bock, Christian Broberger, Karl Deisseroth, Tomas Hökfelt, Sten Linnarsson, Tamas L Horvath, Tibor Harkany. \textbf{Molecular interrogation of hypothalamic organization reveals distinct dopamine neuronal subtypes}. Nature Neuroscience (2016).
        \href{https://dx.doi.org/10.1038/nn.4462}{doi:10.1038/nn.4462}

        \item Clara Jana-Lui Busch, Tim Hendrikx, David Weismann, Sven Jäckel, Sofie M. A. Walenbergh, \underline{André F. Rendeiro}, Juliane Weißer, Florian Puhm, Anastasiya Hladik, Laura Göderle, Nikolina Papac-Milicevic, Gerald Haas, Vincent Millischer, Saravanan Subramaniam, Sylvia Knapp, Keiryn L. Bennett, Christoph Bock, Christoph Reinhardt, Ronit Shiri-Sverdlov, Christoph J. Binder. \textbf{Malondialdehyde epitopes are sterile mediators of hepatic inflammation in hypercholesterolemic mice}. Hepatology (2017).
        \href{https://dx.doi.org/10.1002/hep.28970}{doi:10.1002/hep.28970}

        \item \underline{André F. Rendeiro}*, Christian Schmidl*, Jonathan C. Strefford*, Renata Walewska, Zadie Davis, Matthias Farlik, David Oscier, Christoph Bock. \textbf{Chromatin accessibility maps of chronic lymphocytic leukaemia identify subtype-specific epigenome signatures and transcription regulatory networks}. Nature Communications. 7:11938 (2016).
        \href{https://dx.doi.org/10.1038/ncomms11938}{doi:10.1038/ncomms11938}

        \item Christian Schmidl*, \underline{André F. Rendeiro}*,	Nathan C Sheffield, Christoph Bock. 2015. \textbf{ChIPmentation: fast, robust, low-input ChIP-seq for histones and transcription factors}. Nature Methods (2015).
        \href{https://dx.doi.org/10.1038/nmeth.3542}{doi:10.1038/nmeth.3542}

        \item Michaela Schwaiger, Anna Schönauer, \underline{André F. Rendeiro}, Carina Pribitzer, Alexandra Schauer, Anna Gilles, Johannes Schinko, David Fredman, and Ulrich Technau. \textbf{Evolutionary conservation of the eumetazoan gene regulatory landscape}. Genome Research (2014).
        \href{https://dx.doi.org/10.1101/gr.162529.113}{doi:10.1101/gr.162529.113}

        \end{etaremune}

    \cvitem{\underline{Preprints}}{(does not include preprints later published in peer-reviewed journals)}
        \begin{etaremune}[leftmargin=1.0cm, itemindent=0pt, topsep=10pt, itemsep=2pt, partopsep=0pt, parsep=0pt]

        \item Nathan C. Sheffield, Michał Stolarczyk, Vincent P. Reuter, \underline{André F. Rendeiro}. \textbf{Linking big biomedical datasets to modular analysis with Portable Encapsulated Projects}. bioRxiv (2020).
        \href{https://dx.doi.org/10.1101/2020.10.08.331322}{doi:10.1101/2020.10.08.331322}

        \item Paul Datlinger*, \underline{André F. Rendeiro}*, Thorina Boenke, Thomas Krausgruber, Daniele Barreca, Christoph Bock. \textbf{Ultra-high throughput single-cell RNA sequencing by combinatorial fluidic indexing}. bioRxiv (2019).
        \href{https://dx.doi.org/10.1101/2019.12.17.8793042019}{doi:10.1101/2019.12.17.8793042019}

        \item \underline{André F. Rendeiro}, Pavla  Navratilova, Eric Thompson. \textbf{Chromatin preparation for ChIP-seq in Oikopleura dioica}. Figshare (2014).
        \href{https://dx.doi.org/10.6084/m9.figshare.884562}{doi:10.6084/m9.figshare.884562}

        \end{etaremune}


%----------------------------------------------------------------------------------------
%   CV link
%----------------------------------------------------------------------------------------
\bigskip
\textit{Full Curriculum vitae available at: \href{https://andre-rendeiro.com/cv.pdf}{https://andre-rendeiro.com/cv.pdf}}

%----------------------------------------------------------------------------------------
%   TIMESTAMP
%----------------------------------------------------------------------------------------
\bigskip
\textit{Updated on 2021-07-16}

\end{document}
